---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# costofliving

<!-- badges: start -->
<!-- badges: end -->

## Purpose

The goal of costofliving is to provide functions and data sets to calculate the average cost of living to a single person making minimum wage salaries in different states in the US in 2022. 

## Target Audience

This package targets any working individuals in the US who would like to learn more about whether they find a state livable if they earn minimum wage in that state.


## Installation

You can install the development version of costofliving from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thuntran/costofliving")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(costofliving)
## basic example code
```

Loading the `us_cost_of_living` data set:

```{r us_cost_of_living}
summary(us_cost_of_living)
```


# Contributors

- [Thu Tran](https://github.com/thuntran)
- [Nina Hernandez](http://github.com/nhernandez3)
- [My My Tran](http://github.com/puppehmama)

