---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# costofliving

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/myspotify)](https://CRAN.R-project.org/package=costofliving)
[![R-CMD-check](https://github.com/thuntran/costofliving/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thuntran/costofliving/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Purpose

The goal of `costofliving` is to provide functions and data sets to calculate the average cost of living for a single person earning a minimum wage salary across different states in the United States in 2022. This package contains data from the MIT Living Wage Calculator, The World Population Review, and the Missouri Economic Research and Information Center.

## Target Audience

This package targets any working individuals in the US who would like to learn more about whether they find a state livable if they earn minimum wage in that state.


## Installation

You can install the development version of costofliving from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thuntran/costofliving")
```

## Example

Loading the `costofliving` package:

```{r load-package}
library(costofliving)
```

Loading the `us_cost_of_living` data set:

```{r}
us_cost_of_living
```

Loading the `us_minimum_wage` data set:

```{r}
us_minimum_wage
```

Loading the `us_federal_tax_rate` data set:

```{r}
us_federal_tax_rate
```

Loading the `us_state_local_tax_rate` data set:

```{r}
us_state_local_tax_rate
```

`gross_salary()` is used as a helper function that calculates the annual gross salary of a single person earning minimum wage. It the functionality of other functions:

```{r example-1}
gross_salary("CA")
```

This is an example of how to calculate the amount of federal tax owed by a single person earning minimum wage in a specific state:

```{r example-4}
federal_tax_owed("TN")
```

This is an example of how to calculate the amount of state and local tax owed by a single person earning minimum wage in a specific state:

```{r}
state_local_tax_owed("MS")
```

This is an example of how to calculate the total tax owed and the net salary after tax deductions by a single person earning minimum wage in a specific state:

```{r}
net_salary("TX")
```

This is an example of how to calculate the difference between average cost of living and net salary for a single person earning minimum wage in a specific state:

```{r}
net_salary_avg_col_difference("AL")
```

This is an example of how to calculate gross salary, tax, net salary, and difference between average cost of living and net salary across multiple states of a single person earning minimum wage in a specific state/a few different states:

```{r}
avg_col_multiple_states(c("MA","TX","IL","AL"))
```

This is an example of how to plot the difference in average cost of living and net salary of a single person earning minimum wage in one or multiple states in the USA:

```{r}
avg_col_multiple_states_plot(c("MA","TX","IL","AL"))
```

Plotting the difference in average cost of living and net salary of a single person earning minimum wage across all states in the US:

```{r}
avg_col_multiple_states_plot_all()
```

Here is an example of how to plot the breakdown of the average costs of living for a single person earning minimum wage in a specific state:

```{r}
avg_col_breakdown_plot("WA")
```

# Contributors

- [Thu Tran](https://github.com/thuntran)
- [Nina Hernandez](http://github.com/nhernandez3)
- [My My Tran](http://github.com/puppehmama)

