---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# costofliving

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/myspotify)](https://CRAN.R-project.org/package=costofliving)
<!-- badges: end -->

## Purpose

The goal of `costofliving` is to provide functions and data sets to calculate the average cost of living for a single person earning a minimum wage salary across different states in the United States in 2022. This package also contains data from The World Population Review and the Missouri Economic Research and Information Center. 

## Target Audience

This package targets any working individuals in the US who would like to learn more about whether they find a state livable if they earn minimum wage in that state.


## Installation

You can install the development version of costofliving from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thuntran/costofliving")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r load-package}
library(costofliving)
```

Loading the `us_cost_of_living` data set:

```{r}
us_cost_of_living
```

Loading the `taxable_income` data set:

```{r}
taxable_income
```

Here is a summary of the `us_cost_of_living` data set:

```{r us_cost_of_living}
summary(us_cost_of_living)
```

This is an example of how to calculate the annual gross salary of a single person earning minimum wage in a specific state/a few different states:

```{r example-1}
gross_salary_multiple("MA")
```

```{r example-2}
gross_salary_multiple(c("MA","TX","IL","AL"))
```

# Phase III Package Proposal 

Our R package idea will remain the same, with additional functions and further development for Phase III. We plan to implement two new functions:

  (1) A net_salary() function that calculates the take-home pay (in 2022) for an individual after deducting federal, state, and local taxes from gross salaries based on income tax brackets, per state. 
  
  (2) An avg_living_cost() function that calculates the difference between the net salary and average living cost per state (which includes the average cost of groceries, housing, utilities, transportation, and miscellaneous items). This is essentially the remaining amount of money (if there is) for an individual working minimum wage to financially support themselves in 2022. 
  
  
Besides, we would like to include the following data visualizations:

  (1) Scatter plots to view the average living costs and average net salaries in multiple states (that the user selects).
  
  (2) An interactive USA map where the user can view the average living costs per state using the R leaflet package. 



If there is additional time, we would like to calculate the average living costs per state based on a median household (family of four) where two parents earn minimum wage.


If our package is published, since we are currently using data from 2022 (minimum wage, average living costs, etc) we would expect to make a yearly update. 


# Contributors

- [Thu Tran](https://github.com/thuntran)
- [Nina Hernandez](http://github.com/nhernandez3)
- [My My Tran](http://github.com/puppehmama)

