---
title: "costofliving"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{costofliving}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(costofliving)
library(dplyr)
library(magrittr)
library(purrr)
library(utils)
library(ggplot2)
library(tidyr)
library(forcats)
```

## Purpose

The goal of `costofliving` is to provide functions and data sets to calculate the average cost of living for a single person earning a minimum wage salary across different states in the United States in 2022. This package contains data from the [MIT Living Wage Calculator](https://livingwage.mit.edu/), [the World Population Review](https://worldpopulationreview.com/), [the Nerd Wallet](https://www.nerdwallet.com/article/taxes/federal-income-tax-brackets), and [the Labor Law Center]([https://www.laborlawcenter.com/state-minimum-wage-rates/).

## Target Audience

In general, this package is for anyone interested in the breakdown of average living costs and net salaries across states in the United States. Specifically, this package targets any working individuals in the U.S. who would like to learn more about whether they find a state livable if they a earn minimum wage salary in that state. 

## Example

Loading the `costofliving` package:

```{r load-package}
library(costofliving)
```

## Available Datasets

  + `us_cost_of_living`: A data set containing the average living costs across states in the U.S., including housing, groceries, medical care, etc. in 2022. 
  + `us_minimum_wage`: A data set containing minimum wage across states in the U.S. in 2022.
  + `us_federal_tax_rate`: A data set of the federal tax rates based on income brackets in the U.S. in 2022. 
  + `us_state_local_tax_rate`: A data set of the state and average local tax rates across states in the U.S. in 2022.
  
For consistency, we only provided information on the 50 U.S. states. Thus, District of Columbia and all U.S. territories were excluded. Average living costs for each state were reported as a whole, rather than individual counties or metropolitan areas in that state.

### Loading the `us_cost_of_living` data set:

```{r}
us_cost_of_living
```

### Loading the `us_minimum_wage` data set:

```{r}
us_minimum_wage
```

### Loading the `us_federal_tax_rate` data set:

```{r}
us_federal_tax_rate
```

### Loading the `us_state_local_tax_rate` data set:

```{r}
us_state_local_tax_rate
```

## Available Functions

Note: The functions are able to handle syntax errors if the user inputs an invalid state abbreviation or duplicates of a state.

  + `gross_salary()`: Calculates the annual gross salary of a single person earning minimum wage at a specific state.
  + `federal_tax_owed()`: Calculates the amount of federal tax owed by an individual earning minimum wage based on federal income tax brackets.
  + `state_local_tax_owed()`: Calculates the amount of state and local tax owed by an individual earning minimum wage.
  + `net_salary()`: Calculates the combined tax amount (federal, state, local taxes) for by an individual earning minimum wage, and obtains the net salary by deducting from the gross salary.
  + `net_salary_avg_col_difference()`: Calculates the difference between the average costs of living by the net salary.
  + `avg_col_multiple_states()`: Calculates the annual gross salary, total tax (federal, state, local), net salary, and difference between average cost of living and net salary of a single person earning minimum wage at one or more states.
  + `avg_col_multiple_states_plot()`: Plots the difference in average cost of living and net salary of a single person earning minimum wage at one or more states.
  + `avg_col_multiple_states_plot_all()`: Plots the difference in average cost of living and net salary of a single person earning minimum wage across all states in the USA.
  + `avg_col_breakdown_plot()`: Plots the average cost of living for a single person at a specific state.

### Examples of Function Usage

What is the gross salary for a single person earning minimum wage in California?

```{r example-1}
gross_salary("CA")
```

What is the net salary for a single person earning minimum wage in Texas, after deducting federal, state, and local taxes?

```{r example-2}
net_salary("TX")
```

What is the gross salary, tax amount, net salary, and difference between average cost of living and net salary for a single person earning minimum wage in Alabama?

```{r example-3}
net_salary_avg_col_difference("AL")
```

What are the gross salaries, tax amounts, net salaries, and difference between average cost of living and net salary for a single person earning minimum wage across multiple states (Massachusetts, Texas, Illinois, and Alabama)?

```{r example-4}
avg_col_multiple_states(c("MA", "TX", "IL", "AL"))
```

What is the breakdown of the average cost of living for a single person earning minimum wage in Arizona?

```{r example-7, fig.dim=c(7, 7)}
avg_col_breakdown_plot("AZ")
```

How can I compare the difference in average cost of living and net salary of a single person earning minimum wage in California, Florida, Washington state, and New York state?

```{r example-5, fig.dim=c(7, 5.5)}
avg_col_multiple_states_plot(c("CA", "FL", "WA", "NY"))
```

What is the difference in average cost of living and net salary of a single person earning minimum wage across all states in the U.S.? What are the top five states that are livable to earn a minimum wage salary in?**

```{r example-6, fig.dim=c(7, 6.5)}
avg_col_multiple_states_plot_all()
```

